Prepare National Survey of Early Childhood Health (NSECH) Data 
========================================================
This document preps data (making use of information calculated in `data_prep_CES.Rmd` and `data_prep_ATUS`) from the NSECH. The NSECH data loaded (`datasech.csv`) is a converted version of the file available for download on the CDC website [here](http://www.cdc.gov/nchs/slaits/nsech.htm). The actual data file is in an `*.sd2` format. This is an older SAS format and cannot be read directly into R. This file was downloaded and converted using the SAS system viewer available for free [here](http://www.sas.com/apps/demosdownloads/sassysview_PROD_8.2_sysdep.jsp?packageID=000176). 

```{r prelim_steps_SECH}
#clear memory
rm(list=ls(all=TRUE)) 

setwd("C:/Users/mienkoja/Dropbox/repos/qualpaper/ATUS/2003")
#setwd("C:/Users/mienkoja/Dropbox/qp_analysis/ATUS/2003")
#setwd("~/Dropbox/qualpaper/")

require(sqldf)  	# load the sqldf package (enables sql queries on data frames)

set.seed(123456)

load("C:/Users/mienkoja/Dropbox/repos/qualpaper/cc_out.RData")
load("C:/Users/mienkoja/Dropbox/repos/qualpaper/atus_out.RData")
setwd("C:/Users/mienkoja/Dropbox/repos/qualpaper/")
dat <- read.csv("datasech.csv")
```

Load Variables Required for Analysis
-------------------------
The following script loads all of the variables required in the core analysis of the paper. A preliminary chunk defines a function `coalesce()` which accepts a list of vectors of identical length and returns one vector with the first non-NA value. This script was written by Eric Minikel and is documented in more detail [here](http://www.cureffi.org/2013/05/02/r-equivalent-of-sql-coalesce/). This function is helpful in defining flags across multiple curvey variables (e.g. `dev_cnc` as defined below).


```{r define_coalesce_function}
coalesce = function(...) {
  # convert input arguments into a list of vectors
  input_list = list(...)
  # check that all input vectors are of same length
  vectorlength = length(input_list[[1]])
  for (j in 1:length(input_list)) {
    if(length(input_list[[j]]) != vectorlength) {
      stop(paste("Not all vectors are of same length. First vector length: ",vectorlength,". Vector #",j,"'s length: ",length(input_list[[j]]),sep=""))
    }
  }
  # create a result vector to fill with first non-NA values
  result = rep(NA,vectorlength)
  # fill with first non-NA value
  for (i in 1:length(result)) {
    for (j in 1:length(input_list)) {
      if(!is.na(input_list[[j]][i])) {
        result[i] = input_list[[j]][i]
        break
      }
    }
  }
  return(result)
}
```

Having defined `coalesce()`, we now load all of the variables required for our analysis. These variables roughly mirror those used in previous NSECH reports examining abuse. 

```{r load_req_SECH_vars}

# load adult count
m_adltcnt <- ifelse(as.vector(dat$A7Q01_AR)>=96, NA,as.vector(dat$A7Q01_AR)) 

# load race 
m_race <- ifelse(as.vector(dat$MOMRACER)>=96, NA,as.vector(dat$MOMRACER)) 

#recalc race to white
m_white <- ifelse(m_race==1, 1, ifelse(is.na(m_race)==TRUE, NA, 0))

#load maternal age
m_age <- ifelse(as.vector(dat$A7Q11R)>=96, NA,as.vector(dat$A7Q11R)) 

#load marital status
m_mar_stat <- ifelse(as.vector(dat$A7Q07)>=96, NA,as.vector(dat$A7Q07)) 

#recalc married dummy
m_mar <- ifelse(m_mar_stat==1, 1, ifelse(is.na(m_mar_stat)==TRUE, NA, 0))

#load maternal education
m_ed <- ifelse(as.vector(dat$I_EDUCM)>=96, NA,as.vector(dat$I_EDUCM)) 

#recode to any collegde
m_college <- ifelse(m_ed==3, 1, ifelse(is.na(m_ed)==TRUE, NA, 0))

#load maternal frustration
m_frus <- ifelse(as.vector(dat$A4Q05)>=6, NA,as.vector(dat$A4Q05)) 

#recode to high frustration
m_hi_frus <- ifelse(m_frus<3, 1, ifelse(is.na(m_frus)==TRUE, NA, 0))

#load child health status
c_health <- ifelse(as.vector(dat$A2Q08)>=6, NA,as.vector(dat$A2Q08)) 

#recode to good health
c_hi_health <- ifelse(c_health<3, 1, ifelse(is.na(c_health)==TRUE, NA, 0))

#flag any developmental concern

devq1 <- ifelse(dat$A5Q05X01 <= 2, 1, NA)
devq2 <- ifelse(dat$A5Q05X02 <= 2, 1, NA)
devq3 <- ifelse(dat$A5Q05X03 <= 2, 1, NA)
devq4 <- ifelse(dat$A5Q05X04 <= 2, 1, NA)
devq5 <- ifelse(dat$A5Q05X05 <= 2, 1, NA)
devq6 <- ifelse(dat$A5Q05X06 <= 2, 1, NA)
devq7 <- ifelse(dat$A5Q05X07 <= 2, 1, NA)
devq8 <- ifelse(dat$A5Q05X08 <= 2, 1, NA)
devq9 <- ifelse(dat$A5Q05X09 <= 2, 1, NA)
devq10 <- ifelse(dat$A5Q05X10 <= 2, 1, NA)
devq11 <- ifelse(dat$A5Q05X11 <= 2, 1, NA)

dev_cnc <- coalesce(devq1, devq2, devq3, devq4, devq5, devq6, devq7, devq8, devq9, devq10, devq11) 
dev_cnc[is.na(dev_cnc)] <- 0

#load parental well-being
m_wb1 <- ifelse(as.vector(dat$A5Q01X01)>=96, NA,as.vector(dat$A5Q01X01)) 
m_wb2 <- ifelse(as.vector(dat$A5Q01X02)>=96, NA,as.vector(dat$A5Q01X02)) 
m_wb3 <- ifelse(as.vector(dat$A5Q01X03)>=96, NA,as.vector(dat$A5Q01X03)) 
m_wb4 <- ifelse(as.vector(dat$A5Q01X04)>=96, NA,as.vector(dat$A5Q01X04)) 
m_wb5 <- ifelse(as.vector(dat$A5Q01X05)>=96, NA,as.vector(dat$A5Q01X05)) 

# load child age
c_age <- as.vector(dat$AAP_AGE)

# load income
inc <- as.vector(dat$XBESTINC)

# load reports of positive punishment (yelling)
pospn1 <- ifelse(as.vector(dat$A4Q07X01) > 4, NA, as.vector(dat$A4Q07X01))

# load reports of positive punishment (spanking)
pospn2 <- ifelse(as.vector(dat$A4Q07X02) > 4, NA, as.vector(dat$A4Q07X02))

# load reports of negative punishment (toy takeaway)
negpn1 <- ifelse(as.vector(dat$A4Q07X03) > 4, NA, as.vector(dat$A4Q07X03))

# load reports of negative punishment (time out)
negpn2 <- ifelse(as.vector(dat$A4Q07X04) > 4, NA, as.vector(dat$A4Q07X04))

# load reports of positive punishment (talking about behavior)
pospn3 <- ifelse(as.vector(dat$A4Q07X05) > 4, NA, as.vector(dat$A4Q07X05))

# load reports of safety precautions (gates)
safgt <- ifelse(as.vector(dat$A4Q08X01) > 4, NA, as.vector(dat$A4Q08X01))

# load reports of safety precautions (locks)
saflk <- ifelse(as.vector(dat$A4Q08X02) > 4, NA, as.vector(dat$A4Q08X02))

# load reports of safety precautions (padding)
safpd <- ifelse(as.vector(dat$A4Q08X03) > 4, NA, as.vector(dat$A4Q08X03))

# load reports of safety precautions (block plugs)
safbp <- ifelse(as.vector(dat$A4Q08X04) > 4, NA, as.vector(dat$A4Q08X04))

# load reports of safety precautions (thermostat)
safth <- ifelse(as.vector(dat$A4Q08X05) > 4, NA, as.vector(dat$A4Q08X05))

# load count of children
cnt_ch <- ifelse(as.vector(dat$NUMCHILR) == 97, NA, as.vector(dat$NUMCHILR))

# load reports of reading
read <- data.frame(read=ifelse(as.vector(dat$A4Q02X1R) > 4
                               ,NA
                               ,as.vector(dat$A4Q02X1R)))
# load reports of singing
sing <- data.frame(sing=ifelse(as.vector(dat$A4Q02X2R) > 4
                               ,NA
                               ,as.vector(dat$A4Q02X2R)))

# load reports of transportation (for kids)
trans <- data.frame(trans=ifelse(as.vector(dat$A4Q02X3R) > 4
                                 ,NA
                                 ,as.vector(dat$A4Q02X3R)))

# load reports of dinner 
dinner <- data.frame(dinner=ifelse(as.vector(dat$A4Q02X4R) > 4
                                   ,NA
                                   ,as.vector(dat$A4Q02X4R)))

# load reports of breakfast
breakf <- data.frame(breakf=ifelse(as.vector(dat$A4Q02X5R) > 4
                                   ,NA
                                   ,as.vector(dat$A4Q02X5R)))

# load reports of childcare 
childcare <- ifelse(as.vector(dat$A4Q10R)==995
                    ,0
                    ,ifelse(as.vector(dat$A4Q10R)<995
                            ,as.vector(dat$A4Q10R)
                            ,NA)
                    )

# load reports of childcare setting
care_stg <- as.vector(dat$A4Q12)

# load employment status
emp <- as.vector(dat$A7Q08R)
```

"Smooth" Ordinal and Nominal Variables
-------------------------
In order to complete the proposed analysis, we need to have continuous measures of wealth and of the time spent with children in various activities. The responses from the NSECH do not provide us with this - they provide us with bounded ordinal measures of income. Having defined "priors" from a reasonable income distribution, the American Time Use Survey (ATUS), and the Consumer Expenditure Survey (CES), we can make use of our bounded ordinal measures to sample continuous data into our bounded ordinal measures. At some point, it would be helpful to write a function to help this along. The basic algorithm works as follows: 

1. Define a dataframe with high and low categories from the bounded ordinal measure. 
2. Define a vector of samples from an appropriate prior distribution (as we did in the CES and ATUS scripts).  
3. Loop through each value provided in the survey. 
  * For each value, sample a value from the prior distribution. 
  * For time use measures, sample seperately for different levels of employment. 

The following chunks of code accomplish this task. 

### Smooth Income

```{r smooth_income, tidy=FALSE, cache=TRUE}
# calculate a dataframe with high and low income categories 
inc <- as.data.frame(inc)
inc <- sqldf("select
             inc
             ,case 
             when inc = 1 then 0
             when inc = 2 then 7501
             when inc = 3 then 17501
             when inc = 4 then 25001
             when inc = 5 then 35001
             when inc = 6 then 45001
             when inc = 7 then 60001
             when inc = 8 then 75001
             else null
             end minimum
             ,case 
             when inc = 1 then 7500
             when inc = 2 then 17500
             when inc = 3 then 25000
             when inc = 4 then 35000
             when inc = 5 then 45000
             when inc = 6 then 60000
             when inc = 7 then 75000
             when inc = 8 then 100000
             else null
             end maximum
             from inc")

#create a dataframe with the income prior calculated above
inc_prior <- data.frame(inc_prior=inc_prior)

#extract the maximum value of the income prior and set that value as the upper limit of inc = 8
inc$maximum <- ifelse(inc$maximum==100000, max(inc_prior), inc$maximum)

#calculate the number of observations
obs <- length(inc[,1])

#create an empty vector to hold simulated income values
inc_est <- rep(NA, obs)

#loop through each income value provided in the survey
for (i in 1:obs){
  inc_est[i] <- sample(inc_prior[inc_prior$inc_prior >= inc[i,2] & 
                                   inc_prior$inc_prior <= inc[i,3], ], 1)
}

```

### Smooth Reading

```{r smooth_reading, cache=TRUE, tidy=FALSE}
read <- sqldf("select
              case 
              when read = 1 then 7
              when read = 2 then 3
              when read = 3 then 1
              when read = 4 then 0
              end min_read
              ,case 
              when read = 1 then 7
              when read = 2 then 6
              when read = 3 then 2
              when read = 4 then 0
              end max_read
              from read")

read$emp <- emp

read$min_read <- ifelse(read$min_read == 0, 0
                        ,ifelse(read$min_read > 0
                                ,60/(-read$min_read+8), NA)
)

read$max_read <- ifelse(read$max_read == 0, 0
                        ,ifelse(read$max_read > 0
                                ,60/(-read$max_read+8), NA)
)

read$max_read <- ifelse(read$max_read==60
                        ,max(read_prior_emp)
                        ,read$max_read)

read_prior_emp <- data.frame(read_prior_emp=read_prior_emp)
read_prior_unemp <- data.frame(read_prior_unemp=read_prior_unemp)

read_est <- rep(NA, obs)

for (i in 1:obs){
  if(read[i,3]==1|read[i,3]==2){
    read_est[i] <- sample(read_prior_emp[read_prior_emp$read_prior_emp >= read[i,1] & 
                                           read_prior_emp$read_prior_emp <= read[i,2], ], 1)
  } else if(read[i,3]==3){
    read_est[i] <- sample(read_prior_unemp[read_prior_unemp$read_prior_unemp >= read[i,1] & 
                                             read_prior_unemp$read_prior_unemp <= read[i,2], ], 1)
  } else {
    read_est[i] <- NA
  }
}

```

### Smooth Singing

```{r smooth_singing, cache=TRUE, tidy=FALSE}

sing <- sqldf("select
              case 
              when sing = 1 then 7
              when sing = 2 then 3
              when sing = 3 then 1
              when sing = 4 then 0
              end min_sing
              ,case 
              when sing = 1 then 7
              when sing = 2 then 6
              when sing = 3 then 2
              when sing = 4 then 0
              end max_sing
              from sing")
sing$emp <- emp

sing$min_sing <- ifelse(sing$min_sing == 0, 0
                        ,ifelse(sing$min_sing > 0
                                ,60/(-sing$min_sing+8), NA)
)

sing$max_sing <- ifelse(sing$max_sing == 0, 0
                        ,ifelse(sing$max_sing > 0
                                ,60/(-sing$max_sing+8), NA)
)

sing$max_sing <- ifelse(sing$max_sing==60
                        ,max(sing_prior_emp)
                        ,sing$max_sing)


sing_prior_emp <- data.frame(sing_prior_emp=sing_prior_emp)
sing_prior_unemp <- data.frame(sing_prior_unemp=sing_prior_unemp)

sing_est <- rep(NA, obs)

for (i in 1:obs){
  if(sing[i,3]==1|sing[i,3]==2){
    sing_est[i] <- sample(sing_prior_emp[sing_prior_emp$sing_prior_emp >= sing[i,1] & 
                                           sing_prior_emp$sing_prior_emp <= sing[i,2], ], 1)
  } else if(sing[i,3]==3){
    sing_est[i] <- sample(sing_prior_unemp[sing_prior_unemp$sing_prior_unemp >= sing[i,1] & 
                                             sing_prior_unemp$sing_prior_unemp <= sing[i,2], ], 1)
  } else {
    sing_est[i] <- NA
  }
}
```

### Smooth Transportation

```{r smooth_transport, cache=TRUE, tidy=FALSE}

trans <- sqldf("select
               case 
               when trans = 1 then 7
               when trans = 2 then 3
               when trans = 3 then 1
               when trans = 4 then 0
               end min_trans
               ,case 
               when trans = 1 then 7
               when trans = 2 then 6
               when trans = 3 then 2
               when trans = 4 then 0
               end max_trans
               from trans")
trans$emp <- emp

trans$min_trans <- ifelse(trans$min_trans == 0, 0
                          ,ifelse(trans$min_trans > 0
                                  ,60/(-trans$min_trans+8), NA)
)

trans$max_trans <- ifelse(trans$max_trans == 0, 0
                          ,ifelse(trans$max_trans > 0
                                  ,60/(-trans$max_trans+8), NA)
)

trans$max_trans <- ifelse(trans$max_trans==60
                          ,max(trans_prior_emp)
                          ,trans$max_trans)


trans_prior_emp <- data.frame(trans_prior_emp=trans_prior_emp)
trans_prior_unemp <- data.frame(trans_prior_unemp=trans_prior_unemp)

trans_est <- rep(NA, obs)

for (i in 1:obs){
  if(trans[i,3]==1|trans[i,3]==2){
    trans_est[i] <- sample(trans_prior_emp[trans_prior_emp$trans_prior_emp >= trans[i,1] & 
                                             trans_prior_emp$trans_prior_emp <= trans[i,2], ], 1)
  } else if(trans[i,3]==3){
    trans_est[i] <- sample(trans_prior_unemp[trans_prior_unemp$trans_prior_unemp >= trans[i,1] & 
                                               trans_prior_unemp$trans_prior_unemp <= trans[i,2], ], 1)
  } else {
    trans_est[i] <- NA
  }
}
```

### Smooth Dinner

```{r smooth_dinner, cache=TRUE, tidy=FALSE}

dinner_prior_unemp <- meal_prior_unemp
dinner_prior_emp <- meal_prior_emp

dinner <- sqldf("select
                case 
                when dinner = 1 then 7
                when dinner = 2 then 3
                when dinner = 3 then 1
                when dinner = 4 then 0
                end min_dinner
                ,case 
                when dinner = 1 then 7
                when dinner = 2 then 6
                when dinner = 3 then 2
                when dinner = 4 then 0
                end max_dinner
                from dinner")
dinner$emp <- emp

dinner$min_dinner <- ifelse(dinner$min_dinner == 0, 0
                            ,ifelse(dinner$min_dinner > 0
                                    ,60/(-dinner$min_dinner+8), NA)
)

dinner$max_dinner <- ifelse(dinner$max_dinner == 0, 0
                            ,ifelse(dinner$max_dinner > 0
                                    ,60/(-dinner$max_dinner+8), NA)
)

dinner$max_dinner <- ifelse(dinner$max_dinner==60
                            ,max(dinner_prior_emp)
                            ,dinner$max_dinner)


dinner_prior_emp <- data.frame(dinner_prior_emp=dinner_prior_emp)
dinner_prior_unemp <- data.frame(dinner_prior_unemp=dinner_prior_unemp)

dinner_est <- rep(NA, obs)

for (i in 1:obs){
  if(dinner[i,3]==1|dinner[i,3]==2){
    dinner_est[i] <- sample(dinner_prior_emp[dinner_prior_emp$dinner_prior_emp >= dinner[i,1] & 
                                               dinner_prior_emp$dinner_prior_emp <= dinner[i,2], ], 1)
  } else if(dinner[i,3]==3){
    dinner_est[i] <- sample(dinner_prior_unemp[dinner_prior_unemp$dinner_prior_unemp >= dinner[i,1] & 
                                                 dinner_prior_unemp$dinner_prior_unemp <= dinner[i,2], ], 1)
  } else {
    dinner_est[i] <- NA
  }
}
```

### Smooth Breakfast

```{r smooth_breakfast, cache=TRUE, tidy=FALSE}

breakf_prior_unemp <- meal_prior_unemp
breakf_prior_emp <- meal_prior_emp

breakf <- sqldf("select
                case 
                when breakf = 1 then 7
                when breakf = 2 then 3
                when breakf = 3 then 1
                when breakf = 4 then 0
                end min_breakf
                ,case 
                when breakf = 1 then 7
                when breakf = 2 then 6
                when breakf = 3 then 2
                when breakf = 4 then 0
                end max_breakf
                from breakf")
breakf$emp <- emp


breakf$min_breakf <- ifelse(breakf$min_breakf == 0, 0
                            ,ifelse(breakf$min_breakf > 0
                                    ,60/(-breakf$min_breakf+8), NA)
)

breakf$max_breakf <- ifelse(breakf$max_breakf == 0, 0
                            ,ifelse(breakf$max_breakf > 0
                                    ,60/(-breakf$max_breakf+8), NA)
)

breakf$max_breakf <- ifelse(breakf$max_breakf==60
                            ,max(breakf_prior_emp)
                            ,breakf$max_breakf)


breakf_prior_emp <- data.frame(breakf_prior_emp=breakf_prior_emp)
breakf_prior_unemp <- data.frame(breakf_prior_unemp=breakf_prior_unemp)

breakf_est <- rep(NA, obs)

for (i in 1:obs){
  if(breakf[i,3]==1|breakf[i,3]==2){
    breakf_est[i] <- sample(breakf_prior_emp[breakf_prior_emp$breakf_prior_emp >= breakf[i,1] & 
                                               breakf_prior_emp$breakf_prior_emp <= breakf[i,2], ], 1)
  } else if(breakf[i,3]==3){
    breakf_est[i] <- sample(breakf_prior_unemp[breakf_prior_unemp$breakf_prior_unemp >= breakf[i,1] & 
                                                 breakf_prior_unemp$breakf_prior_unemp <= breakf[i,2], ], 1)
  } else {
    breakf_est[i] <- NA
  }
}
```

### Combine Time Estimates

This section binds all of the time use estimates into a single dataframe and sums in order to calculate a total annual hours committed to children (`t_ca`)

```{r combine_time_est, cache=TRUE, tidy=FALSE}
#clean up RAM
gc()

t_c <- data.frame(read=read_est
                  ,sing=sing_est
                  ,trans=trans_est
                  ,dinner=dinner_est
                  ,breakf=breakf_est)
t_c <- rowSums(t_c)
t_ca <- t_c*365.25/60
```

Estimate an Annual Childcare Expenditure
-------------------------
Here I use estimates from the consumer expenditure survey to calculate an estimated childcare expenditure per year based on the maternal responses in the SECH. Here, the mothers responded with an actual number of hours that children spend in childcare during a given week (`childcare`). I use a different distribution (i.e. `cc_own`, `cc_ctr`, or `cc_oth`) depending on the care setting (`care_stg`) indicated by the mother. 

```{r cc_est, cache=TRUE, tidy=FALSE}
# bind relevant variables into a dataframe
childcare <- data.frame(childcare = childcare)
childcare$care_stg <- care_stg

# create an empty vector 
x_c <- rep(NA, obs)

#childcare*(cc_cost/4/40)*52 = 0.29575*cc_cost*childcare

# loop through every survey value
for (i in 1:obs){
  if(!is.na(childcare[i,2]) & childcare[i,2]==1){
    x_c[i] <- childcare[i,1]*(cc_own/4/40)*52
  } else if(!is.na(childcare[i,2]) & childcare[i,2]==2){
    x_c[i] <- childcare[i,1]*(cc_oth/4/40)*52  
  } else if(!is.na(childcare[i,2]) & childcare[i,2]==3){
    x_c[i] <- childcare[i,1]*(cc_ctr/4/40)*52
  } else {
    x_c[i] <- childcare[i,1]*(mean(c(cc_ctr, cc_oth, cc_own))/4/40)*52
  }
}
```


Define Key Economic and Dependent Variables for analysis
-------------------------

```{r key_vars, cache=TRUE, tidy=FALSE}
# next calculate an hourly wage for the parents using the mc work hour sims from atus                                  

hrs_est <- rep(NA, obs)
for (i in 1:obs){
  hrs_est[i] <- ifelse(emp[i]==1, sample(x=mc_hrs_ft, size=1, replace=TRUE),
                       ifelse(emp[i]==2, sample(x=mc_hrs_pt, size=1, replace=TRUE), 
                              ifelse(emp[i]==3|emp[i]==4, 0, NA)))
}

#wage from income (w_i) (hourly)
w_i <- (inc_est/m_adltcnt)/(365.25*hrs_est)

#calculate the child time multiplier (w_i for working mothers, market rate for childcare otherwise)
cc_mlt <- ifelse(w_i == Inf, 104/31, w_i)

#calculate alpha (constraining values to below 1...this only effects 18 values)
#alpha <- log(t_ca*cc_mlt + x_c)/log((cc_mlt*365.25*24))
#alpha <- ifelse(alpha > 1, 1, alpha)
alpha <- (t_ca*cc_mlt + x_c)/((cc_mlt*365.25*24))
alpha <- ifelse(alpha > 1, 1, alpha)

#wage from endowment (w_e) (annual)
w_ea <- ifelse(w_i==Inf, inc_est, 0) 

#recode wealth from income (annual)
w_ia <- w_i*40*52

#total wealth from income and endowments
w_ta <- inc_est 

#total time available (minus work hours)
t_ta <- (24*365.25)-hrs_est

#total time value available
t_tva <- t_ta*w_i

#total time value spent on children using the Reid (1934) standard 
#outlined in A Framework for Nonmarket Accounting
t_tvc <- t_ca*cc_mlt

#implicit time value spent on parent
t_tvp <- t_tva-t_tvc

#time value for the whole year
#for working parents multiply by w_i
#if w_i not available, multiply by mean(cc_own, cc_oth, cc_ctr)
t_v <- w_i * 365*24

# load reports of negative punishment (toy takeaway)
negpn1 <- ifelse(as.vector(dat$A4Q07X03) > 4, NA, as.vector(dat$A4Q07X03))

# load reports of negative punishment (time out)
negpn2 <- ifelse(as.vector(dat$A4Q07X04) > 4, NA, as.vector(dat$A4Q07X04))

# load reports of positive punishment (talking about behavior)
pospn3 <- ifelse(as.vector(dat$A4Q07X05) > 4, NA, as.vector(dat$A4Q07X05))

#recode yelling
pospn1_bin <- ifelse(pospn1 < 4, 1, 0)

#recode spanking
pospn2_bin <- ifelse(pospn2 < 4, 1, 0)

#recode toy takeaway
negpn1_bin <- ifelse(negpn1 < 4, 1, 0)

#recode time-out
negpn2_bin <- ifelse(negpn2 < 4, 1, 0)

#recode talking about behavior
pospn3_bin <- ifelse(pospn3 < 4, 1, 0)

#recode gate safety gates
safgt_bin <- ifelse(safgt == 3 | safgt == 7, NA
                    ,ifelse(safgt == 1, 1, 0)
                    )

#recode gate safety locks
saflk_bin <- ifelse(saflk == 3 | saflk == 7, NA
                    ,ifelse(saflk == 1, 1, 0)
)

#recode padding precautions
safpd_bin <- ifelse(safpd == 3 | safpd == 7, NA
                    ,ifelse(safpd == 1, 1, 0)
)

#recode gate safety plug blocks
safbp_bin <- ifelse(safbp == 3 | safbp == 7, NA
                    ,ifelse(safbp == 1, 1, 0)
)


# recode thermostat safety
safth_bin <- ifelse(safth == 3 | safth == 7, NA
                    ,ifelse(safth == 1, 1, 0)
)

```


Pull Key Variables Together
-------------------------

```{r combine_vars, tidy=FALSE}

r_dat <- data.frame(id=seq(1:2068)
                    ,c_age
                    ,cnt_ch
                    ,m_white 
                    ,m_age
                    ,m_mar 
                    ,m_college
                    ,m_hi_frus
                    ,c_health 
                    ,c_hi_health                    
                    ,dev_cnc
                   ,w_ta
                   ,t_ta
                   ,t_tvc
                   ,x_c
                   ,inc_est
                   ,t_ca
                   ,cc_mlt
                   ,x_c
                   ,pospn1_bin
                   ,pospn1
                   ,pospn2_bin
                   ,pospn2
                   ,negpn1_bin
                   ,negpn1
                   ,negpn2_bin
                   ,negpn2
                   ,pospn3_bin
                   ,pospn3
                   ,safgt_bin
                   ,safgt
                   ,saflk_bin
                   ,saflk
                   ,safpd_bin
                   ,safpd
                   ,safbp_bin
                   ,safbp
                   ,safth_bin
                   ,safth
                   ,alpha)
```

Calculate Probability of All Negative Discipline
-------------------------

```{r calc_p_all_neg, tidy=FALSE}
pospn1_bin0 <- pospn1_bin
pospn2_bin0 <- pospn2_bin
pospn3_bin0 <- pospn3_bin
negpn1_bin0 <- negpn1_bin
negpn2_bin0 <- negpn2_bin

safgt_bin0 <- safgt_bin
safpd_bin0 <- safpd_bin
saflk_bin0 <- saflk_bin
safbp_bin0 <- safbp_bin
safth_bin0 <- safth_bin

pospn1_bin0[is.na(pospn1_bin0)] <- 0
pospn2_bin0[is.na(pospn2_bin0)] <- 0
pospn3_bin0[is.na(pospn3_bin0)] <- 0
negpn1_bin0[is.na(negpn1_bin0)] <- 0
negpn2_bin0[is.na(negpn2_bin0)] <- 0
safgt_bin0[is.na(safgt_bin0)] <- 0
safpd_bin0[is.na(safpd_bin0)] <- 0
saflk_bin0[is.na(saflk_bin0)] <- 0
safbp_bin0[is.na(safbp_bin0)] <- 0
safth_bin0[is.na(safth_bin0)] <- 0

pos_count <- rowSums(data.frame(pospn1_bin0, pospn2_bin0, pospn3_bin0))
neg_count <- rowSums(data.frame(negpn1_bin0, negpn2_bin0))
pos_count_alt1 <- rowSums(data.frame(pospn1_bin0, pospn2_bin0))
neg_count_alt1 <- rowSums(data.frame(negpn1_bin0, negpn2_bin0, pospn3_bin0))
pos_count_alt2 <- rowSums(data.frame(pospn1_bin0, pospn2_bin0))
neg_count_alt2 <- rowSums(data.frame(negpn1_bin0, negpn2_bin0))
saf_count <- rowSums(data.frame(safgt_bin0, safpd_bin0, saflk_bin0, safbp_bin0, safth_bin0))

dis_strat <- data.frame(id=seq(1:obs)
                        ,dis_strat=rep(NA, obs)
                        ,pos_count
                        ,neg_count
                        ,pos_count_alt1
                        ,neg_count_alt1
                        ,pos_count_alt2
                        ,neg_count_alt2
                        ,saf_count)
for (i in 1:obs){
  if(pos_count[i]>0 & neg_count[i]==0){
    dis_strat[i,2] <- 0
  }else if(neg_count[i]>0 & pos_count[i]==0){
    dis_strat[i,2] <- 1
  }else{
    dis_strat[i,2] <- "mixture"
  }  
}

r_dat <- sqldf("select 
               r.*
               ,pos_count
               ,neg_count
               ,pos_count_alt1
               ,neg_count_alt1
               ,pos_count_alt2
               ,neg_count_alt2
               ,saf_count
               from r_dat r
               join dis_strat ds
               on r.id=ds.id")

#rm(list=setdiff(ls(), "r_dat"))
save.image("C:/Users/mienkoja/Dropbox/repos/qualpaper/sech_out.RData")
```
